Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-18 krs-survey.tex
Extended with ref to psychology + added figure to the Memory section

Memory has been studied at lenght in the cognitive neuroscience community, and
the ability to forget is proven to play a key role for the cognition.
\fxwarning{Add references -> ask Claire or Gladys}.

Most knowledge representation systems offers some kind of working memory as a
pool of facts that are not forgotten by the robot until it is halted. Some
systems may propose persistent storages that allow the robot knowledge to grow
over time, while other may offer a larger range of memory categories, like
short term memory (that last for a couple of seconds) or episodic memory (that
allows the robot to selectively remember facts associated to specific events).
\fxwarning{Add references of paper in the robotics community that have
explicitely tackled the memory issue}.

>>>>

Memory has been studied at lenght in the cognitive psychology and
neuropsychology communities: Atkinson and Shiffrin~\cite{Atkinson1968}
introduce the idea of \emph{short-term} and \emph{long-term} memory,
Anderson~\cite{Anderson1976} splits memory into \emph{declarative} (explicit)
and \emph{procedural} (implicit) memories, Tulving~\cite{Tulving1985} organizes
the concepts of \emph{procedural}, \emph{semantic} and \emph{episodic} memories
into a hierarchy. Short-term memory is refined with the concept of
\emph{working memory} by Baddeley~\cite{Baddeley2010}
(Figure~\ref{fig|memory_models}).

\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{memory_models.pdf}
    \caption{Overview of the main types of memories}
    \label{fig|memory_models}
\end{figure}

Most knowledge representation systems offers some kind of memory as a pool of
facts that are not forgotten by the robot until it is halted (this memory is
often refered as a \emph{working memory}, but with a meaning unrelated to
Baddeley's definition). Some systems may propose persistent storages that allow
the robot knowledge to grow over time, while other may offer a larger range of
memory categories, like short term memory (that lasts for a couple of seconds)
or episodic memory (that allows the robot to selectively remember facts
associated to specific events).
